Supplementary Materials

### 2023-07-04 manuscript/manuscript.tex
ms changes

Our composite likelihood method has three sets of parameters: expected
diversity in the absence of linked selection diversity $\pi_0$, the mutation
rate $\mu$, and the distribution of fitness effects $\mathbf{W}$ across the
selection grid for each of the $K$ feature types. Given that the relationship
between $\pi$ and the strength selection is U-shaped, we wondered whether the
observed genome-wide patterns of diversity could fit under weaker selection
than found in previous methods based on classic BGS theory.

@@

\subsection*{Predicted Diversity Substitution Rates}

\begin{figure}[htbp] \centering
    \includegraphics[width=\textwidth]{figures/figure_5.pdf} 
    \caption{}
  \label{fig:figure-4}
\end{figure}

>>>>

Our composite likelihood method has three sets of parameters: expected
diversity in the absence of linked selection diversity $\pi_0$, the mutation
rate $\mu$, and the distribution of fitness effects $\mathbf{W}$ across the
selection grid for each of the $K$ feature types. Given that the relationship
between $\pi$ and the strength selection is U-shaped, we wondered whether the
observed genome-wide patterns of diversity could be explained by weaker
selection than found in previous methods based on classic BGS theory.

@@

\subsection*{Predicted Diversity, Substitution Rates, and Fitness Variance}

\begin{figure}[htbp] \centering
    \includegraphics[width=\textwidth]{figures/figure_5.pdf} 
    \caption{}
  \label{fig:figure-5}
\end{figure}

### 2023-07-04 manuscript/supplementary.tex
ms changes

\caption{$R^2$ and mutation rate estimates for all models. Note that the repeated values in the last 
rows are correct and due to rounding; see \path{notebooks/main_fits.ipnb} in the GitHub repository for 
more information.}

@@

@@

>>>>

\caption{$R^2$ and mutation rate estimates for all primary models (top table)
    and models fit on a smaller DFE grid (excluding the possibility of strong
    selection $s=10^{-1}$). Note that the repeated values in the last rows are
    correct and due to rounding; see \path{notebooks/main_fits.ipynb} in the
    GitHub repository for more information.}

@@

\emph{smaller DFE grid} & & & & & & \\
\textbf{phastcons$>$CDS$>$genes}  &              full &          YRI &               \textbf{67.27} &             67.36 &             &                                 2.0333 &                                \\
               CADD 6\%  &            sparse &          YRI &                        66.66 &             66.81 &             &                                 1.6565 &                                \\
               CADD 6\%  &              full &          YRI &                        66.50 &             66.68 &             &                                 1.5556 &                                \\
CDS$>$genes$>$phastcons  &              full &          YRI &                        63.61 &             64.28 &             &                                 3.3493 &                                \\
\textbf{phastcons$>$CDS$>$genes}  &              full &          CEU &               \textbf{61.04} &             62.25 &             &                                 1.9128 &                                \\
               CADD 6\%  &            sparse &          CEU &                        60.37 &             61.80 &             &                                 1.6797 &                                \\
               CADD 6\%  &              full &          CEU &                        60.24 &             61.77 &             &                                 1.6347 &                                \\
               \textbf{phastcons$>$CDS$>$genes}  &     full &          CHB &                        \textbf{58.76} &             60.45 &             &                                 1.8691 &                                \\
               CADD 6\%  &            sparse &          CHB &                        58.67 &             60.49 &             &                                 1.7454 &                                \\
               CADD 6\%  &              full &          CHB &                        58.48 &             60.40 &             &                                 1.5981 &                                \\
CDS$>$genes$>$phastcons  &              full &          CEU &                        57.24 &             59.11 &             &                                 3.0461 &                                \\
CDS$>$genes$>$phastcons  &              full &          CHB &                        55.63 &             57.88 &             &                                 3.1723 &                                \\

@@

\begin{figure}[htbp] \centering
    \includegraphics[width=0.5\textwidth]{figures/supplementary/subfigure_R2_scale.pdf}
    \caption{XXX}
  \label{suppfig:coal_r2_scale}
\end{figure}
